\documentclass[
  fontsize=10pt,
  twoside=true,
  numbers=noenddot,
  overfullrule=false,
]{kaobook}

\usepackage[english]{babel}
\usepackage[english=american]{csquotes}

\usepackage{kaobiblio}
\addbibresource{main.bib}

\usepackage{mdftheorems}
\usepackage{qmtheorems}

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{svg.path}
% To set the width of a tikz picture
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}%
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}
\makeatother

% Be able to suppress line numbers in listings
\let\origthelstnumber\thelstnumber
\makeatletter
\newcommand*\suppresslinenumbers{%
  \lst@AddToHook{OnNewLine}{%
    \let\thelstnumber\relax%
     \advance\c@lstnumber-\@ne\relax%
    }%
}

\newcommand*\reactivatelinenumbers{%
  \lst@AddToHook{OnNewLine}{%
   \let\thelstnumber\origthelstnumber%
   \advance\c@lstnumber\@ne\relax}%
}
\makeatother

% Reset sidenote counter at chapters
\counterwithin*{sidenote}{chapter}

\begin{document}

\titlehead{A Full Course in Software Engireering}

\title[]{Becoming an Engineer}
\subtitle{From Soup to Nuts: Level 1}

\author[]{Joshua Reyes}

\date{\small\today}

\publishers{Lee Street Publishing}

\frontmatter
% copyright page
\makeatletter
\uppertitleback{\@titlehead} % Header

\lowertitleback{
	\textbf{Disclaimer}\\
	You can edit this page to suit your needs. For instance, here we have a no copyright statement, a colophon and some other information. This page is based on the corresponding page of Ken Arroyo Ohori's thesis, with minimal changes.

	\medskip

	\textbf{No copyright}\\
	\cczero\ This book is released into the public domain using the CC0 code. To the extent possible under law, I waive all copyright and related or neighbouring rights to this work.

	To view a copy of the CC0 code, visit: \\\url{http://creativecommons.org/publicdomain/zero/1.0/}

	\medskip

	\textbf{Colophon} \\
	This document was typeset with the help of \href{https://sourceforge.net/projects/koma-script/}{\KOMAScript} and \href{https://www.latex-project.org/}{\LaTeX} using the \href{https://github.com/fmarotta/kaobook/}{kaobook} class.

	The source code of this book is available at:\\\url{https://github.com/jareyes/qm-companion}

	(You are welcome to contribute!)

	\medskip

	\textbf{Publisher} \\
	First printed in April 2020 by \@publishers
}
\makeatother

% Dedication page
\dedication{``A clever person solves a problem. A wise person avoids it.'' --- Almost certainly not Albert Einstein
\vskip 15pt
For everyone trying to keep afloat.
}

\KOMAoptions{twoside=semi}
\maketitle
\KOMAoptions{twoside=true}

% Preface
\input{chapters/preface.tex}
% Table of conents
\etocstandarddisplaystyle % "toc display" as if etoc was not loaded
\etocstandardlines % "toc lines as if etoc was not loaded
\tableofcontents

\mainmatter % Denotes the start of the main document content, resets page numbering and uses arabic numbers
\setchapterstyle{kao} % Choose the default chapter heading style
\input{chapters/introduction.tex}
% \input{chapters/things.tex}

\pagelayout{wide} % No margins
\addpart{Solutions to Problems}
\pagelayout{margin} % Restore margins

\setcounter{chapter}{0}
\renewcommand{\thechapter}{\Alph{chapter}}
\input{solutions/introduction.tex}


\backmatter
% The bibliography needs to be compiled with biber using your LaTeX editor, or on the command line with 'biber main' from the template directory
\defbibnote{bibnote}{Here are the references in citation order.\par\bigskip} % Prepend this text to the bibliography
\printbibliography[heading=bibintoc, title=Bibliography, prenote=bibnote] % Add the bibliography heading to the ToC, set the title of the bibliography and output the bibliography note


\end{document}
