\chapter{\label{chapter:intro} Introduction}

Programming languages are implemented in programs. In particular, JavaScript is implemented by its interpreter. So we'll need to install a JavaScript interpreter in order to run the JavaScript programs we write. But in order to run the interpreter, we need another program\sidenote{Actually, a very large collection of programs} that will run the intepreter: the operating system. We will also need another program, a text editor, to write and edit our programs in. \marginnote{From \textit{Rapanos vs United States}: In our favored version, an Eastern guru affirms that the earth is supported on the back of a tiger. When asked what supports the tiger, he says it stands upon an elephant; and when asked what supports the elephant he says it is a giant turtle. When asked, finally, what supports the giant turtle, he is briefly taken aback, but quickly replies ``Ah, after that it is turtles all the way down.''}In order to write and run programs we need many other programs. It's programs all the way down.

\begin{itemize}
  \item Operating system: any flavor of Unix. I am using Ubuntu 20.04 on my personal laptop. Just about any version of Linux or MacOS will do. For now, this book does not support Microsoft Windows. In the future it may.
  \item Web Browser: Mozilla Firefox 86.0.1 or Ubuntu. Since we will be using web browsers only briefly, it doesn't much matter which of the major browsers you use. All of them implement the core features of JavaScript we'll be using.
  \item JavaScript implementation: Node.js is an open-source general-purpose implementation and extension of JavaScript. It was originally intended to create fast, scalable network applications for the web. We will be using Node.js version 14. At the time of writing, version 16 is already available for preview but has not been released for production use yet. Before this book has started, it is already obselete.
  \item Text editor: I will be using Atom with some vanilla language highlighting and nothing more. Atom is a full-fledged integrated development environment (IDE). I use it, however, as a plain text editor. I do not enable autocomplete, automatic build processes, or other magic, albeit useful, programming conveniences. As you develop your programming muscle memory, these niceties may increase your productivity. At the beginning, however, they tend to stymie learning and understanding by burying all the interesting bits under the hood.
\end{itemize}

You should already have a operating system and web browser installed on your computer. We will set up Node.js and Atom together.

\section{Web Browser Interpreter}

\section{Command Line}

\section{Node.js}
